Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-02 reports/manuscript.Rmd
Fix manuscript rendering

```{r, load-targets}
targets::tar_load(c(
  "manuscript_info", "combined_bib", "reviews_tables", "combined_bib", "plots"
),
store = here::here("_targets")
)
```

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

```{r prisma, fig.cap="PRISMA Diagram"}
knitr::include_graphics(here::here("figure", "PRISMA Diagram.pdf"))
```

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

```{r desctable}
reviews_tables$kable$data %>%
  knitr::kable("latex",
    caption = "Review characteristics for studies providing unique effects",
    col.names = c(
      "First Author", "Year", "Design Restrictions",
      "Regions Restrictions", "Study Range",
      "Sample Age Restrictions",
      "Outcomes Assessed", "Exposures Assessed"
    ),
    escape = FALSE,
    booktabs = TRUE,
    align = c("l", "c", "l", "l", "c", "l", "l", "l"),
    linesep = "",
    longtable = TRUE
  ) %>%
  kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::column_spec(3:4, width = "2cm") %>%
  kableExtra::column_spec(5, width = "1.5cm") %>%
  kableExtra::column_spec(6:8, width = "3cm") %>%
  kableExtra::kable_styling(
    latex_options = c("repeat_header"),
    font_size = 5
  ) %>%
  kableExtra::landscape()
```

The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.

@@

```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
plots[[1]]$plot
```

@@

```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
plots[[2]]$plot
```

>>>>

```{r, load-targets}
targets::tar_load(
  c(
    "manuscript_info", "combined_bib", "plots", "prisma", "table_desc_latex",
    "edu_certain_params", "plot_edu_certain",
    "nonedu_certain_params", "plot_nonedu_certain"
  ),
  store = here::here("_targets")
)
```

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab::desctable)).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

```{r prisma, fig.cap="PRISMA Diagram"}
knitr::include_graphics("../figures/PRISMA Diagram.pdf", error = FALSE)
```

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table \@ref(tab::desctable).
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

```{r desctable}
table_desc_latex %>%
  knitr::kable(
    "latex",
    caption = "Review characteristics for studies providing unique effects",
    col.names = c(
      "First Author", "Year", "Design Restrictions",
      "Regions Restrictions", "Study Range",
      "Sample Age Restrictions",
      "Outcomes Assessed", "Exposures Assessed"
    ),
    escape = FALSE,
    booktabs = TRUE,
    align = c("l", "c", "l", "l", "c", "l", "l", "l"),
    linesep = "",
    longtable = TRUE
  ) %>%
  kableExtra::row_spec(1:nrow(table_desc_latex), hline_after = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::column_spec(3:4, width = "2cm") %>%
  kableExtra::column_spec(5, width = "1.5cm") %>%
  kableExtra::column_spec(6:8, width = "3cm") %>%
  kableExtra::kable_styling(
    latex_options = c("repeat_header"),
    font_size = 5
  ) %>%
  kableExtra::landscape()
```

The quality of the included meta-analyses was mixed (see Table \@ref(tab::desctable)).
Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.

@@

```{r eduplot, fig.width=edu_certain_params$dims[[1]], fig.height=edu_certain_params$dims[[2]], fig.cap="Education outcomes"}
plot_edu_certain
```

@@

```{r healthplot, fig.width=nonedu_certain_params$dims[[1]], fig.height=nonedu_certain_params$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
plot_nonedu_certain
```
